Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-05-27 awipev-CO2.Rmd
update pCO2 plot

# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
# noaa <- noaa %>%
#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
#   unite("datetime", c("date", "time"), sep=" ")
#  
# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
# noaa <- noaa %>%
#  dplyr::filter(datetime > "2015-07-01 00:00:00")
# 
# 
# poster_pco2 <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
#   geom_point(data=d_all, aes(x=datetime, y=pco2calc), col="red" )+
#   geom_point() +geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value),size=0.5 ) +
#   scale_color_manual("",values=c("red", "blue", "black"), labels=c("pH spectro", "seaFET EXT ", "seaFET EXT corrected"))+
#   labs(x = "", y ="", title = expression(paste(italic(p),CO[2]," (µatm)"))) +
#   theme_bw() + theme(legend.position= c(0.59, 0.1),
#                      legend.text=element_text(size=14),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
#                      axis.text=element_text(size=15),
#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# print(poster_pco2)
# ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

>>>>

noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
noaa <- noaa %>%
  dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
  unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
  unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
  unite("datetime", c("date", "time"), sep=" ")

noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
noaa <- noaa %>%
 dplyr::filter(datetime > "2015-07-01 00:00:00")

#create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
           "Calculated from AT/CT",
          expression(paste(italic(p),CO[2]," (ppm; NOAA)"))
          )

col <- c("blue","red","green")

poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
  geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="green" ),size=0.5)+
  scale_shape_discrete(labels=lab, guide="none")+
  scale_colour_manual(labels=lab, values=col)+
  labs(x = "", y ="", title = "") +
  theme_bw() +
  scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position= c(0.18, 0.85),
                     legend.text=element_text(size=14, colour="black"),
                     #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
                     axis.text=element_text(size=15),
                     plot.margin = unit(c(0.5,1,1,1), "cm"),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank()
                     ) 
print(poster_pco2)
 # ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
